Source Summaries

### 2020-02-09 paper/sourceSummaries/summary2.tex
Updated my summary

\noindent
The authors directly compare different authentication methods using different factors.  These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.

@@

\noindent
The authors found that each system has individual strengths.  As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.  Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.

>>>>

\noindent
The authors directly compare different authentication methods using different factors using factors that would matter to a user in addition to the overall security of the system.  For user factors, factors considered include include battery life, ease of use and what happens if a credential is misplaced, stolen or forgotten.  As for security, factors considered included the a user passing off a credential to an unauthorized party, the ability to spoof a credential, and the ease of bypass for a mechanical system.

@@

\noindent
The authors find that no one current system could be considered the most secure, and that each system has individual strengths.  As each method does better in different ways, emphasis should be instead placed on ensuring the use of the lock that is most suited for the use case in which it is placed.
